Binocular integration of chromatic and luminance signals

### 2024-04-02 manuscript.qmd
Hopefully fixed python issue

if (processdata>0){
  # install_python(version="3.9.19")
  # use_python_version("3.9.19")
  use_python('/usr/bin/python3.9')
  # install_miniconda()
  # use_miniconda('r-reticulate')
  # py_install('pip')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

>>>>

if (processdata>0){
  install_python(version="3.6")
  # use_python_version("3.9.19")
  # use_python('/usr/bin/python3.9')
  # install_miniconda()
  # use_miniconda('r-reticulate')
  # py_install('pip')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}
